---
title: "Beer variables Vs Style"
author: "vincent trouillet"
date: "5 juin 2018"
output: ioslides_presentation
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## overview

This was built as part of a deliverable for the course Developing Data Products as part of the Coursera Data Science Specialization.

The app developed for the first part of the assignment demo is avalilable at: 
https://thetrouille.shinyapps.io/ShinyAssign/

Source code for ui.R and server.R files are available on the GitHub repo:
https://github.com/vtrouill/ShinyAssignement
 


## Beer Dataset (1/2)

```{r beer, echo =  FALSE}
setwd("ShinyAssign")
beer<-read.csv("BeerRecipesST101.csv")
```
```{r beer2, echo = FALSE}
str(beer)
```

## Beer Dataset (2/2)

there are eight style of beer (american IPA, American brown Ale, imperial IPA, Irish Red Ale, Belgian Specialty Ale, witbier, saison and Russian Imperial Stout).

3 variables will be considered for the application : ABV (alcohol in %), IBU (bitterness), and COLOR ( Morey formula)


## the application


The application displays the behaviour of a variable in relation to the style of beer for different types of figure (boxplot, histogram and density)

The variable visualized and the type of figure is left to the user's choice.
